Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-02-17 paper/main.tex
fixing the appendix

\item
\citep{Libeskind2013} %various alignments
Studies shape and spin alignment with the cosmic web defined by the
velocity shear tensor method described in this paper.

The simulation has $2048^3$ particles in a box of $250$\hMpc,
corresponding to a particles mass of $1.3\times 10^{8}$\hMsun.  Halos
are found using a FOF halo finder with $b=0.17$. The catalog only
include halos more massiven than $3\times 10^{9}$\hMsun.

The shape is defined from the reduced inertia tensor. Results are
reported for three mass bins $M_{\rm vir}<10^{11.5}$\hMsun,
$11^{11.5}<M_{\rm vir}<12^{12.5}\hMsun$ and $M_{\rm
  vir}>12^{12.5}\hMsun$.

The identification of the cosmic web is done on a grid of $256^3$ with
a gaussian smoothing of $\sim 1$\hMpc over the velocity field. We
define this velocity field as the ratio of a momentum density to the
matter density field. The details of this approach are described in
the Appendix .

The aligmnet signal of the spin is very weak while the shape alignment
signal is very strong. The shape alignment is such that the eigenvector
corresponding to the smallest eigenvalue is aligned with the major
axis. This effect is stronger for more massive halos. 
In other words the major axis of a halo is aligned with a filament,
and lies on the plane that define a sheet. However the spin is
antialgined with the filament for massive halos and weakly aligned for
low mass halos.

>>>>

\item
\citep{Libeskind2013} %various alignments
Studies shape and angular momentum alignments with the cosmic web
defined by the velocity shear tensor method described in this
paper.

\cite{Libeskind2013} also used the Bolshoi simulation and the halo
catalogs we use in this work. Results are reported for three mass bins $M_{\rm
  vir}<10^{11.5}$\hMsun, $11^{11.5}<M_{\rm vir}<12^{12.5}\hMsun$ and
$M_{\rm  vir}>12^{12.5}\hMsun$.   The identification of the cosmic web
is done on a grid of $256^3$ with a gaussian smoothing of $\sim
1$\hMpc over the velocity field. The way they compute this smoothed
velocity field differs from our computation. We do it based on the
momentum density field while \cite{Libesking2013} do not take into
account the mass in each cell.

The aligmnet signal for the angular momentum is very weak while the shape alignment
signal is very strong. The shape alignment is such that the eigenvector
corresponding to the smallest eigenvalue is aligned with the major
axis. This effect is stronger for more massive halos. 
In other words the major axis of a halo is aligned with a filament,
and lies on the plane that define a sheet. The angular momentum is
anti-aligned with the filament for massive halos and weakly aligned
for low mass halos.
